A Bayesian networks approach to infer social changes in burials in northeastern Taiwan during the European colonization period

### 2021-05-04 analysis/paper/paper.Rmd
edit the caption of figure 3 and color the ties

```{r figure-network-diagrams, fig.cap = "A: Burial network before the European arrival, B: Burial network after the European arrival. The size of each node is proportional to node degrees or the number of connections to a node. The thickness of ties represents the number of goods in common between two nodes."}
knitr::include_graphics(here::here("analysis", "figures", "005-network-diagrams.png"))
```

>>>>

```{r figure-network-diagrams, fig.cap = "A: Burial network before the European arrival, B: Burial network after the European arrival. The size of each node is proportional to node degrees or the number of connections to a node. The thickness of ties represents the number of goods in common between two nodes. Isolated nodes are not displayed in the plots"}
knitr::include_graphics(here::here("analysis", "figures", "005-network-diagrams.png"))
```
